Pool Model

### 2023-12-20 pool_model.tex
make sure to specify that this is not really the total nutrients

Both of these species grow using limiting resource pool $R$ with different growth constants $\alpha$ and different lengths of lag phase determined by parameter $\lambda$.

@@

        \dot{L_A} = -\lambda_A R L_A\\
        \dot{G_A} = \lambda_A R L_A + \alpha_A R G_A\\
        \dot{L_B} = -\lambda_B R L_B\\
        \dot{G_B} = \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B\\

@@

        \dot{R} = -\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R G_B \\

>>>>

Both of these species grow using limiting resource pool $R^*$ with different growth constants $\alpha$ and different lengths of lag phase determined by parameter $\lambda$.
It has to be noted that the resource pool is normalized by its initial value, ie $R^* = R/R_0$.

@@

        \dot{L_A} = -\lambda_A R^* L_A\\
        \dot{G_A} = \lambda_A R^* L_A + \alpha_A R^* G_A\\
        \dot{L_B} = -\lambda_B R^* L_B\\
        \dot{G_B} = \lambda_B R^* L_B + \frac{\alpha_B}{1 + \mu_I I} R^* G_B\\

@@

        \dot{R^*} = -\frac{\alpha_A}{N_t} R^* G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R^* G_B \\
